Think deep for reef resilience

### 2025-08-15 paper/paper_draft.qmd
Correct number of connectivity/spawning days represented

Connectivity data from 24 days in total were used in this investigation. These data span six
years from 2015 to 2020. The years 2015, 2016, 2018 and 2019 are each represented by
connectivity matrices covering spawning periods over three days in each year (12 days in
total), while 2017 and 2020 are each represented by five spawning days each, coming to a
total of 22 days of connectivity matrices. Indicative connectivity strengths are implemented
in ADRIA-CoralBlox as the mean of all available data for each location (i.e., mean of all 22
spawning days). While the connectivity strengths do not vary from year to year within each
simulation, they do vary between reefs whiuch are of varying sizes, providing sufficient
heterogeneity to capture spatial patterns in larval dispersal and settlement dynamics. The
spatial variability also enables investigations into the influence of connectivity strength
and its role in driving recovery processes.

>>>>

Connectivity data from 24 days in total were used in this investigation. These data span six
years from 2015 to 2020. The years 2015, 2016, 2018 and 2019 are each represented by
connectivity matrices covering spawning periods over three days in each year (12 days in
total), while 2017 and 2020 are each represented by six spawning days each, coming to a
total of 24 days of connectivity matrices. Indicative connectivity strengths are implemented
in ADRIA-CoralBlox as the mean of all available data for each location (i.e., mean of all 24
spawning days). While the connectivity strengths do not vary from year to year within each
simulation, they do vary between reefs which are of varying sizes, providing sufficient
heterogeneity to capture spatial patterns in larval dispersal and settlement dynamics. The
spatial variability also enables investigations into the influence of connectivity strength
and its role in driving recovery processes.
